Implicit yaddayadda

### 2011-10-26 papers/PLDI2012/implicitization.tex
experiments

@@

The analysis using disjunctive invariants seems not to be as efficient as
expected, and often finds greater invariants than the combined technique
($11.64\%$). It probably means that our heuristic for the construction of
$\sigma$ is not effective.

@@

>>>>

For the computation of disjunctive invariants, we experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\cite{DBLP:conf/pldi/GulwaniZ10}.  We start with one sigle
disjunct per control point ($m=1$), and we start with an empty map $\sigma$. We also
define a maximal bound on the number of disjunct per control point, noted $M$.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the convex hull of the two abstract values is
exactly the union of them. If such an index exists, then $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

@@

The analysis using disjunctive invariants seems not to be as efficient as
expected, and often finds greater invariants than the combined technique
($11.64\%$). It probably means that our heuristic for the construction of
$\sigma$ is not effective enough. Usually, disjunctive invariants computation
finds precise loop invariants because they allow to distinguish for
instance the first loop iterations. In our case, such benefits are not
visible, since we have already unrolled every loops once.

@@

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} technique are sometimes faster than the classical
algorithm. Our techniques are slower, but on the same order of magnitude than
the previous techniques.
